Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-09-02 paper/paper.tex
latest referee reply

{\bf \tol\ presents a \lya emission line with puzzling fetures.}
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

>>>>

{\bf \tol\ presents a \lya emission line with puzzling features.}
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.
